Speed and strength of epidemic intervention

### 2019-07-24 doc/speedstrength.tex
minor tweak

As our baseline scenario, we assume that early transmission is responsible for 23\% of the total transmission \citep{hayes2006amplified}.
Based on the growth rate estimate ($0.452 \textrm{year}^{-1}$) from a HIV prevalence data in pregnant women in South Africa \citep{barron2013eliminating}, our baseline reproduction number is $3.17$.
Increasing the amount of early transmission reduces the mean generation time, which in turn decreases the reproduction number.

\begin{figure}
\includegraphics[width=\textwidth]{../figure/figure1.pdf}
\caption{This is not a figure.}
\end{figure}

>>>>

As our baseline scenario (\figref{example}A), we assume that early transmission is responsible for 23\% of the total transmission \citep{hayes2006amplified}.
Based on the growth rate estimate ($0.452 \textrm{year}^{-1}$; \figref{example}B) from a HIV prevalence data in pregnant women in South Africa \citep{barron2013eliminating}, our baseline reproduction number is $3.17$.
Further increasing the amount of early transmission reduces the mean generation time, which in turn decreases the reproduction number (\figref{example}C).

\begin{figure}
\includegraphics[width=\textwidth]{../figure/figure1.pdf}
\caption{This is not a figure.}
\figlab{example}
\end{figure}
